Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-03-02 epidemics_manuscript/outbreak_response_models_review_v2.tex

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Outbreak response interventions to human vaccine-preventable diseases: a systematic review of modelling practices before COVID-19}
}
\newline
\\
James M. Azam\textsuperscript{1*},
Xiaoxi Pang\textsuperscript{2},
Elisha B. Are\textsuperscript{1, 3},
Juliet R.C. Pulliam\textsuperscript{1},
Matthew J. Ferrari\textsuperscript{4}
\\
\bigskip
\textbf{1} DSI-NRF Centre of Excellence in Epidemiological Modelling and Analysis (SACEMA), Stellenbosch University, Stellenbosch 7600, South Africa
\\
\textbf{2} Department of Mathematics, The University of Manchester, Manchester, UK
\\
\textbf{3} Department of Mathematics, Simon Fraser University, Burnaby, BC, Canada
\\
\textbf{4} Center for Infectious Disease Dynamics, Department of Biology, The Pennsylvania
State University, University Park, Pennsylvania, USA
\\
\bigskip

### 2023-03-15 analyses/scripts/full_data_extraction_citation_table.Rmd
updated the global chunk settings

---
output:
  pdf_document:
    keep_tex: yes
---

```{r echo=FALSE, include=FALSE}
#' load packages
library('tidyverse')
library('readr')
library('xlsx')
library('scales')
library('stringr')
library('conflicted')
library('Hmisc')
library('kableExtra')

>>>>

---
output:
  pdf_document:
    keep_tex: yes
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
options(kableExtra.auto_format = FALSE)

knitr::opts_chunk$set(echo = FALSE, 
                      include = FALSE,
                      dev = 'jpeg', 
                      fig.width = 8, 
                      fig.height = 6, 
                      message = FALSE
                      )
```

```{r}
#' load packages
library('tidyverse')
# library('xlsx')
library('scales')
library('stringr')
library('conflicted')
library('Hmisc')
library('kableExtra')
